Create CHaMP map

### 2020-06-03 analysis/R_scripts/compile_wtsd_bndry.Rmd
re-did map of CHaMP watersheds, adding a north arrow and saving map in 4 different formats.

# load packages for analysis
library(tidyverse)
library(janitor)
library(magrittr)
library(sf)
library(ggrepel)

@@

```{r}
ggplot(data = champ_wtsds) +
  geom_sf() +
  geom_sf(data = champ_wtsds %>%
            filter(fish_data),
          fill = 'black') +
  geom_sf_label(aes(label = id),
                position = position_dodge(width = 200)) +
                # position = position_nudge(x = 5000,
                #                           y = -5000)) +
  theme(axis.title = element_blank())

@@

>>>>

# load packages for analysis
library(tidyverse)
library(janitor)
library(magrittr)
library(sf)
library(ggrepel)
library(ggspatial)

@@

```{r}
ggplot(data = champ_wtsds) +
  geom_sf() +
  geom_sf(data = champ_wtsds %>%
            filter(fish_data),
          fill = 'black') +
  geom_sf_label(aes(label = id),
                position = position_dodge(width = 200)) +
                # position = position_nudge(x = 5000,
                #                           y = -5000)) +
  annotation_north_arrow(location = 'tr',
                         which_north = 'true',
                         style = north_arrow_fancy_orienteering) +
  theme(axis.title = element_blank())

@@

Now let's make a map that we can import into the manuscript

```{r}
champ_wtsds = read_rds('../data/derived_data/champ_wtds.rds')
river_lines = QRFcapacity::get_flowlines(stream_order = 6,
                                         champ_wtsds %>%
                                           st_union() %>%
                                           st_make_grid(n = 1)) %>%
            filter(!grepl('^1701', reachcode),
                   !grepl('^171', reachcode))

# river_lines %>%
#   filter(!gnis_name %in% c('Deschutes River',
#                            'Crooked River',
#                            'Payette River',
#                            'North Fork Payette River')) %>%
#   ggplot() +
#   geom_sf(aes(color = gnis_name))

wtsd_map = ggplot(data = champ_wtsds) +
  geom_sf(data = river_lines %>%
            filter(!gnis_name %in% c('Deschutes River',
                                     'Crooked River',
                                     'Payette River',
                                     'North Fork Payette River')),
          color = 'darkblue') +
  geom_sf() +
  geom_sf(data = champ_wtsds %>%
            filter(fish_data),
          fill = 'black') +
  geom_sf_label(aes(label = id),
                position = position_dodge(width = 200)) +
  annotation_north_arrow(location = 'tr',
                         which_north = 'true',
                         style = north_arrow_fancy_orienteering) +
  theme(axis.title = element_blank())

# save a couple versions
ggsave('../figures/ChampWtds.svg',
       wtsd_map,
       dpi = 600,
       height = 6,
       width = 6)
ggsave('../figures/ChampWtds.png',
       wtsd_map,
       dpi = 600,
       height = 6,
       width = 6)
ggsave('../figures/ChampWtds.tiff',
       wtsd_map,
       dpi = 600,
       height = 6,
       width = 6)
ggsave('../figures/ChampWtds.jpeg',
       wtsd_map,
       dpi = 600,
       height = 6,
       width = 6)
```
